Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-06 ms/SI.Rmd
Use custom function for generating comm matrix at different grain sizes
uses less memory than phyloregion::points2comm

loadd(list = c(
  "richness_by_res",
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

# Summarize redundancy statistics by grain size
redundancy_summary <-
  richness_by_res %>%
  mutate(above_50 = ifelse(redundancy > 0.5, 1, 0)) %>%
  mutate(singleton = ifelse(redundancy == 0, 1, 0)) %>%
  group_by(res) %>%
  summarize(
    n_total = n(),
    n_above_50 = sum(above_50),
    n_singletons = sum(singleton),
    percent_above_50 = n_above_50/n_total,
    percent_singletons = n_singletons/ n_total,
    .groups = "drop"
  )

@@

# Distribution of redundancy by grain size
c <- ggplot(redund_by_res, aes(x = redundancy, y = res)) +
  geom_density_ridges(scale = 1.5) + 
  scale_y_discrete(expand = c(0, 0), labels = degree_lab) +     # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  labs(
    x = "Redundancy",
    y = "Resolution"
  )

>>>>

loadd(list = c(
  "comm_scaled_list_0.1",
  "comm_scaled_list_0.2",
  "comm_scaled_list_0.3",
  "comm_scaled_list_0.4",
  "richness_by_res",
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

# Combine results of building community matrices at different grain sizes
redundancy_by_res <- 
  list(
    "0.1" = comm_scaled_list_0.1$poly_shp,
    "0.2" = comm_scaled_list_0.2$poly_shp,
    "0.3" = comm_scaled_list_0.3$poly_shp,
    "0.4" = comm_scaled_list_0.4$poly_shp) %>%
  map_df(~as_tibble(.) %>% select(grids, abundance, richness), .id = "res") %>%
  # Calculate redundancy
  mutate(redundancy = 1 - (richness/abundance))

# Summarize redundancy statistics by grain size
redundancy_summary <-
  redundancy_by_res %>%
  mutate(above_50 = ifelse(redundancy > 0.5, 1, 0)) %>%
  mutate(singleton = ifelse(redundancy == 0, 1, 0)) %>%
  group_by(res) %>%
  summarize(
    n_total = n(),
    n_above_50 = sum(above_50),
    n_singletons = sum(singleton),
    percent_above_50 = n_above_50/n_total,
    percent_singletons = n_singletons/ n_total,
    .groups = "drop"
  )

@@

# Distribution of redundancy by grain size
c <- ggplot(redundancy_by_res, aes(x = redundancy, y = res)) +
  geom_density_ridges(scale = 1.5) + 
  scale_y_discrete(expand = c(0, 0), labels = degree_lab) +     # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  labs(
    x = "Redundancy",
    y = "Resolution"
  )
